{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-07 Paper/main.tex
Two added outlook points
Adiing bspline_fpcr results, structuring application

	\section{Application}\label{Application}
		The application uses the methods and insights from the previous sections to predict the octane ratings of the introduced gasoline dataset.
		Although the simulation study granted valuable insights in the different methods in four different settings, it is not enough to determine the method and choice of basis of the application from those insights, since there is still too much uncertainty involved. To point out some sources of uncertainty: First, opposing to the simulations study, we do not know the true coefficient function. The insights from just two functions, $f_1$ and $f_2$, is not enough to draw any conclusion. Second, we do not know anything about the signal-to-noise ratios of the measured octane numbers. Third, we made assumptions about the distribution of $\xi$ that are not relateable to this real-life application where we not know this distribution, neither can we infer something about it. We will run all specification again for the gasoline dataset, but the results from the simulation study will contribute towards the reading of the results. The application is designed similar to the simulation study: The 60 spectra of the gasoline dataset will be used to regress them on the reported octane numbers and evaluate the results as prediction MSE using 10 fold cross-validation. In total, we conducted 1000 repetitions for each setting.
	\subsection{Interpretation of Results}

	\nocite{carey_life_2002}

>>>>

	\section{Application}\label{Application}
		The application uses the methods and insights from the previous sections to predict the octane ratings of the introduced gasoline dataset.
		Although the simulation study granted valuable insights in the different methods in four different settings, it is not enough to determine the method and choice of basis of the application, since there is too much uncertainty involved. To point out some sources of uncertainty: First, opposing to the simulation setup, we do not know the true coefficient function. The insights from just two functions, $f_1$ and $f_2$, is not enough to draw any conclusion. Second, we have no information about the signal-to-noise ratios of the measured octane numbers. Third, we made assumptions about the distribution of $\xi$ that are not relateable to this real-life application where we not know this distribution, neither can we infer something about it. 
		Therefore, we will run all specification again for the gasoline dataset and use the results of the simulation study towards the reading of the results. The application is designed similar to the simulation study: The 60 spectra of the gasoline dataset will be used to regress them on the reported octane numbers and evaluate the results as prediction MSE using 12 fold cross-validation with 5 elements per fold. In total, we conducted 1000 repetitions for each setting.

	\subsection{Interpretation of Results}
		\subsubsection{Basis Expansion Regression}
		\subsubsection{Functional Principal Component Regression}

	%\nocite{carey_life_2002}
